Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2020-11-02 main.tex
:construction: Update diagonal index

			where $k_i=i_s/i!(nv_t)^i$. It can be observed that the traditional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$. However, due to the coupling among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power. In other words, even-order terms with $i \ge 4$ account for the nonlinear behavior of the diode. For simplicity, we let $\beta_2={k_2}{R_{\text{ant}}}$, $\beta_4={k_4}{R_{\text{ant}}^2}$ and choose $n_0=4$ to investigate fundamental rectifier nonlinearity so that $z$ further reduces to \eqref{eq:z_expand}. Note that $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^2\right\}=1$ but $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current. Inspired by \cite{Huang2017}, we stack up channel and waveform vectors over all subbands as $\boldsymbol{h}=[\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$ and $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^T,\dots,\boldsymbol{w}_{I/P,N}^T]^T \in \mathbb{C}^{MN \times 1}$. Let $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$. On top of this, we introduce $\boldsymbol{W}_{I/P,n} \in \mathbb{C}^{MN \times MN}$ ($n=-N+1,\dots,N-1$) that can be viewed as $N \times N$ blocks, each of size $M \times M$. As illustrated by Fig.~\ref{fi:block_diagonal}, let $\boldsymbol{W}_{I/P,n}$ keep the $n$-th block diagonal of $\boldsymbol{W}_{I/P}$ and null all other blocks.

			% \begin{figure}[!t]
			% 	\begin{equation*}
			% 		\resizebox{0.9\linewidth}{!}{
			% 			$\boldsymbol{W}_{I/P}=
			% 			\left(
			% 				\begin{array}{cccc}
			% 					\cellcolor[gray]{0.5}\boldsymbol{w}_{I/P,1}\boldsymbol{w}_{I/P,1}^H & \cellcolor[gray]{0.7}\boldsymbol{w}_{I/P,1}\boldsymbol{w}_{I/P,2}^H & \dots                                                                 & \cellcolor[gray]{0.9}\boldsymbol{w}_{I/P,1}\boldsymbol{w}_{I/P,N}^H   \\
			% 					\cellcolor[gray]{0.7}\boldsymbol{w}_{I/P,2}\boldsymbol{w}_{I/P,1}^H & \cellcolor[gray]{0.5}\boldsymbol{w}_{I/P,2}\boldsymbol{w}_{I/P,2}^H & \cellcolor[gray]{0.7}\ddots                                           & \vdots                                                                \\
			% 					\vdots                                                              & \cellcolor[gray]{0.7}\ddots                                         & \cellcolor[gray]{0.5}\ddots                                           & \cellcolor[gray]{0.7}\boldsymbol{w}_{I/P,N-1}\boldsymbol{w}_{I/P,N}^H \\
			% 					\cellcolor[gray]{0.9}\boldsymbol{w}_{I/P,N}\boldsymbol{w}_{I/P,1}^H & \dots                                                               & \cellcolor[gray]{0.7}\boldsymbol{w}_{I/P,N}\boldsymbol{w}_{I/P,N-1}^H & \cellcolor[gray]{0.5}\boldsymbol{w}_{I/P,N}\boldsymbol{w}_{I/P,N}^H
			% 				\end{array}
			% 			\right)$
			% 		}
			% 	\end{equation*}
			% 	\caption{$\boldsymbol{W}_{I/P,n}$ keeps the $n$-th block diagonal of $\boldsymbol{W}_{I/P}$ and nulls the remaining entries. Solid, dashed and dotted diagonals correspond to $n>,=,<0$. For $\boldsymbol{w}_{I/P,n_1}\boldsymbol{w}_{I/P,n_2}^H$, the $n$-th diagonal satisfies $n_2-n_1=n$.}
			% 	\label{fi:block_diagonal}
			% \end{figure}

@@

						\end{tikzpicture}
				\end{equation*}
				\caption{$\boldsymbol{W}_{I/P}$ consists of $N \times N$ blocks of size $M \times M$. $\boldsymbol{W}_{I/P,k}$ keeps the $k$-th block diagonal of $\boldsymbol{W}_{I/P}$ and nulls all remaining blocks. Solid, dashed and dotted blocks correspond to $n>0$, $n=0$ and $n<0$, respectively. For $\boldsymbol{w}_{I/P,n_1}\boldsymbol{w}_{I/P,n_2}^H$, the $k$-th block diagonal satisfies $k=n_2-n_1$.}
				\label{fi:block_diagonal}
			\end{figure*}

			On top of this, we define $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H \in \mathbb{C}^{MN \times MN}$ and let $\boldsymbol{W}_{I/P,n} \in \mathbb{C}^{MN \times MN}$ keep their $n$-th ($n=-N+1,\dots,N-1$) block diagonal and set all other blocks to $\boldsymbol{0}^{M \times M}$.

			null the remaining entries, where the blocks are of size $M \times M$. On top of this, relevant DC terms are expressed in \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
			\begin{figure*}[b]
				\hrule
				\begin{equation}
					z(\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho) = \beta_2\rho\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)\,.\label{eq:z_expand}
				\end{equation}
				\hrule
				\begin{flalign}
					\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h}\,,&&\label{eq:y_I2}\\
					\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}
					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h})^2\,,&&\label{eq:y_I4}
				\end{flalign}
				\begin{align}
					\mathcal{A}\left\{y_{P}^2(t)\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{P,0}\boldsymbol{h}\,,\label{eq:y_P2}\\
					\mathcal{A}\left\{y_{P}^4(t)\right\}
					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{P,{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{P,{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{P,{n_3}})^H(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{P,{n_4}})^H} = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})^H\,.\label{eq:y_P4}
				\end{align}
			\end{figure*}
		\end{subsection}

@@

			In this section, the IRS phase shift $\boldsymbol{\phi}$ is optimized for any given waveform $\boldsymbol{w}_{I/P}$ and splitting ratio $\rho$. We observe that for $n=1,\dots,N$,

@@

			where $t$ is an auxiliary variable with unit modulus, $\boldsymbol{M}_n=[\boldsymbol{V}_n^H, \boldsymbol{h}_{D,n}]^H \in \mathbb{C}^{(L+1) \times M}$, $\bar{\boldsymbol{\phi}}=[\boldsymbol{\phi}^H, t]^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi}=\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n = \boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$. Also, for $n=-N+1,\dots,N-1$, define $t_{I/P,n}$ as

@@

				t_{I/P,n}
				& = \boldsymbol{h}^H\boldsymbol{W}_{I/P,n}\boldsymbol{h}\nonumber\\
				& = \mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{I/P,n})\nonumber\\
				& = \mathrm{Tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{I/P,n}\right)\nonumber\\
				& = \mathrm{Tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{I/P,n})\nonumber\\
				& = \mathrm{Tr}(\boldsymbol{M}\boldsymbol{W}_{I/P,n}\boldsymbol{M}^H\boldsymbol{\Phi})\nonumber\\
				& = \mathrm{Tr}(\boldsymbol{C}_{I/P,n}\boldsymbol{\Phi})

@@

			where $\boldsymbol{V}=[\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M}=[\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{I/P,n}=\boldsymbol{M}\boldsymbol{W}_{I/P,n}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$. Therefore, the rate and objective expressions rewrite as

@@

				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{I,0}^2 + \sum_{n=-N+1}^{N-1}{t_{P,n}t_{P,n}^*}\right)\nonumber\\

@@

				t_{P,n}^{(i)} (t_{P,n}^{(i)})^*
				& \ge 2 \Re\left\{t_{P,n}^{(i)} (t_{P,n}^{(i-1)})^*\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\,,\label{eq:taylor_2}\\

@@

					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(4 (t_{I,0}^{(i)})(t_{I,0}^{(i-1)}) - 2 (t_{I,0}^{(i-1)})^2 + \sum_{n=-N+1}^{N-1}{2 \Re\left\{t_{P,n}^{(i)} (t_{P,n}^{(i-1)})^*\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*}\right)\nonumber\\

@@

			When $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}, the optimal phase shift vector $\bar{\boldsymbol{\phi}}^\star$ can be obtained by Eigenvalue Decomposition (EVD). Otherwise, a suboptimal solution can be extracted via Gaussian randomization method \cite{Huang2010}. Specifically, we perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$, generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$, construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, and choose the one that maximizes the objective function \eqref{ob:irs}. Finally, the phase shift is retrieved by $\theta_l^{\star}=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$. The SCA algorithm for passive beamforming optimization is summarized in Algorithm~\ref{al:irs}.
			\begin{algorithm}[!t]
				\caption{SCA: IRS Phase Shift.}
				\label{al:irs}
				\begin{algorithmic}[1]
					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h}_{D,n},\boldsymbol{H}_{I,n},\boldsymbol{h}_{R,n},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho,\sigma_n,\bar{R},Q,\epsilon$
					\State Construct $\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n}$ for $n=1,\dots,N$, $\boldsymbol{C}_{I/P,n}$ for $n=-N+1,\dots,N-1$
					\State \textbf{initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{I/P,n}^{(0)}$ for $n=-N+1,\dots,N-1$
					\Repeat
						\State $i \gets i + 1$
						\State Obtain $\boldsymbol{\Phi}^{(i)}, t_{I/P,n}^{(i)}$ by solving problem~\eqref{op:irs}
						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
					\If{$\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$}
						\State Obtain $\bar{\boldsymbol{\phi}}^\star$ by EVD, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
					\Else
						\State Obtain $\boldsymbol{U},\boldsymbol{\Sigma}$ by EVD, $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$
						\State Generate $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $q=1,\dots,Q$
						\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$
						\State Set $q^{\star}=\arg\max_q{z(\boldsymbol{\Phi}_q)}$, $\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
					\EndIf
					\State Set $\theta_l^\star=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$, and construct $\boldsymbol{\phi}^{\star}$
					\State \textbf{output} $\boldsymbol{\phi}^{\star}$
				\end{algorithmic}
			\end{algorithm}
		\end{subsection}

>>>>

			where $k_i=i_s/i!(nv_t)^i$. It can be observed that the traditional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$. However, due to the coupling among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power. In other words, even-order terms with $i \ge 4$ account for the nonlinear behavior of the diode. For simplicity, we let $\beta_2={k_2}{R_{\text{ant}}}$, $\beta_4={k_4}{R_{\text{ant}}^2}$ and choose $n_0=4$ to investigate fundamental rectifier nonlinearity so that $z$ further reduces to \eqref{eq:z_expand}. Note that $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^2\right\}=1$ but $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current. Inspired by \cite{Huang2017}, we stack up channel and waveform vectors over all subbands as $\boldsymbol{h}=[\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$ and $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^T,\dots,\boldsymbol{w}_{I/P,N}^T]^T \in \mathbb{C}^{MN \times 1}$. On top of this, let $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H \in \mathbb{C}^{MN \times MN}$. As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{I/P}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{I/P,k}$ keep its $k$-th ($k=-N+1,\dots,N-1$) block diagonal and set all other blocks to $\boldsymbol{0}^{M \times M}$. Hence, the components of the output DC current $z$ can be expressed in \eqref{eq:y_I2} -- \eqref{eq:y_P4}.

@@

						\end{tikzpicture}
				\end{equation*}
				\caption{$\boldsymbol{W}_{I/P}$ consists of $N \times N$ blocks of size $M \times M$. $\boldsymbol{W}_{I/P,k}$ keeps the $k$-th block diagonal of $\boldsymbol{W}_{I/P}$ and nulls all remaining blocks. Solid, dashed and dotted blocks correspond to $k>0$, $k=0$ and $k<0$, respectively. For $\boldsymbol{w}_{I/P,n_1}\boldsymbol{w}_{I/P,n_2}^H$, the $k$-th block diagonal satisfies $k=n_2-n_1$.}
				\label{fi:block_diagonal}
			\end{figure*}

			\begin{figure*}[b]
				\hrule
				\begin{equation}
					z(\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho) = \beta_2\rho\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)\,.\label{eq:z_expand}
				\end{equation}
				\hrule
				\begin{flalign}
					\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h}\,,&&\label{eq:y_I2}\\
					\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}
					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h})^2\,,&&\label{eq:y_I4}
				\end{flalign}
				\begin{align}
					\mathcal{A}\left\{y_{P}^2(t)\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{P,0}\boldsymbol{h}\,,\label{eq:y_P2}\\
					\mathcal{A}\left\{y_{P}^4(t)\right\}
					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{P,{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{P,{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{P,{n_3}})^H(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{P,{n_4}})^H} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{P,k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{P,k}\boldsymbol{h})^H\,.\label{eq:y_P4}
				\end{align}
			\end{figure*}
		\end{subsection}

@@

			In this section, the IRS phase shift $\boldsymbol{\phi}$ is optimized for any given waveform $\boldsymbol{w}_{I/P}$ and splitting ratio $\rho$. We observe that

@@

			where $t$ is an auxiliary variable with unit modulus, $\boldsymbol{M}_n=[\boldsymbol{V}_n^H, \boldsymbol{h}_{D,n}]^H \in \mathbb{C}^{(L+1) \times M}$, $\bar{\boldsymbol{\phi}}=[\boldsymbol{\phi}^H, t]^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi}=\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n = \boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$. On the other hand, we define $t_{I/P,k}$ as

@@

				t_{I/P,k}
				& = \boldsymbol{h}^H\boldsymbol{W}_{I/P,k}\boldsymbol{h}\nonumber\\
				& = \mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{I/P,k})\nonumber\\
				& = \mathrm{Tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{I/P,k}\right)\nonumber\\
				& = \mathrm{Tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{I/P,k})\nonumber\\
				& = \mathrm{Tr}(\boldsymbol{M}\boldsymbol{W}_{I/P,k}\boldsymbol{M}^H\boldsymbol{\Phi})\nonumber\\
				& = \mathrm{Tr}(\boldsymbol{C}_{I/P,k}\boldsymbol{\Phi})

@@

			where $\boldsymbol{V}=[\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M}=[\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{I/P,k}=\boldsymbol{M}\boldsymbol{W}_{I/P,k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$. Therefore, the rate and objective expressions rewrite as

@@

				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{I,0}^2 + \sum_{k=-N+1}^{N-1}{t_{P,k}t_{P,k}^*}\right)\nonumber\\

@@

				t_{P,k}^{(i)} (t_{P,k}^{(i)})^*
				& \ge 2 \Re\left\{t_{P,k}^{(i)} (t_{P,k}^{(i-1)})^*\right\} - t_{P,k}^{(i-1)} (t_{P,k}^{(i-1)})^*\,,\label{eq:taylor_2}\\

@@

					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(4 (t_{I,0}^{(i)})(t_{I,0}^{(i-1)}) - 2 (t_{I,0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 \Re\left\{t_{P,k}^{(i)} (t_{P,k}^{(i-1)})^*\right\} - t_{P,k}^{(i-1)} (t_{P,k}^{(i-1)})^*}\right)\nonumber\\

@@

			When $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}, the optimal phase shift vector $\bar{\boldsymbol{\phi}}^\star$ can be obtained by Eigenvalue Decomposition (EVD). Otherwise, a suboptimal solution can be extracted via Gaussian randomization method \cite{Huang2010}. Specifically, we perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$, generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$, construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, and choose the one that maximizes the objective function \eqref{ob:irs}. Finally, the phase shift is retrieved by $\theta_l^{\star}=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$. The SCA algorithm for passive beamforming optimization is summarized in Algorithm~\ref{al:irs}.
			\begin{algorithm}[!t]
				\caption{SCA: IRS Phase Shift.}
				\label{al:irs}
				\begin{algorithmic}[1]
					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h}_{D,n},\boldsymbol{H}_{I,n},\boldsymbol{h}_{R,n},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho,\sigma_n,\bar{R},Q,\epsilon$
					\State Construct $\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n}$, $\boldsymbol{C}_{I/P,k}$, $\forall n,k$
					\State \textbf{initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{I/P,k}^{(0)}, \forall k$
					\Repeat
						\State $i \gets i + 1$
						\State Obtain $\boldsymbol{\Phi}^{(i)}, t_{I/P,k}^{(i)}$ by solving problem~\eqref{op:irs}
						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
					\If{$\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$}
						\State Obtain $\bar{\boldsymbol{\phi}}^\star$ by EVD, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
					\Else
						\State Obtain $\boldsymbol{U},\boldsymbol{\Sigma}$ by EVD, $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$
						\State Generate $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $q=1,\dots,Q$
						\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$
						\State Set $q^{\star}=\arg\max_q{z(\boldsymbol{\Phi}_q)}$, $\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
					\EndIf
					\State Set $\theta_l^\star=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$, and construct $\boldsymbol{\phi}^{\star}$
					\State \textbf{output} $\boldsymbol{\phi}^{\star}$
				\end{algorithmic}
			\end{algorithm}
		\end{subsection}
